The Weakly Nonlinear Magnetorotational Instability in a local geometry

### 2017-03-24 paper/thingap_ref_response/thingap_mri_paper_ref_response_apj.tex

\begin{figure}
\centering
\includegraphics[width=\columnwidth]{thingap_stressfig_Pm_1E-2}
\caption{\edit1{Total (Reynolds + Maxwell) stress in the domain as predicted from the weakly nonlinear theory for $\Pm=1E-2$.}} \label{fig:wnl_stress}
\end{figure}

>>>>

\begin{figure}
\centering
\includegraphics[width=\columnwidth]{thingap_stressfig_Pm_1E-2}
\caption{\edit1{Total (Reynolds + Maxwell) stress in the domain as predicted from the weakly nonlinear theory at $\Pm = 10^{-2}$.}} \label{fig:wnl_stress}
\end{figure}
